Title Goes Here

### 2022-12-14 analysis/paper/paper.qmd
fixing description

```{r}
#| label: setup
library(minTEMU)

>>>>

```{r}
#| label: setup
library(dplyr)
library(readr)
devtools::load_all(".")

# read csv file with pages that are useful for the analysis
emu_theses <- read_csv(here::here("analysis","data", "raw_data", "emu-theses.csv")) %>%
  mutate(pdf_filename = paste0(year, "-", author_surname, ".pdf")) %>%
  mutate(text = "")

pdf_paths<- here::here("analysis","data", "raw_data", emu_theses$pdf_filename)

emu_theses$text <- convert_pdf_text(pdf_paths)
